---
title: "CENTREprecomputed"
author: "Sara Lopez Ruiz de Vargas"
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{CENTRE ExperimentHub datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteDepends{CENTREprecomputed,RSQLite,BiocStyle,ExperimentHub}
output: 
  BiocStyle::html_document
link-citations: true
---

# CENTREprecomputed: An ExperimentHub package with the precomputed data and example data for CENTRE

**CENTRE** is a package for Cell-type specific ENhancer Target pREdiction, that 
follows this workflow: 

`createPairs()` -> `computeGenericFeatures()` -> `computeCellTypeFeatures()` -> `centreClassification()`

The step `CENTRE::computeGenericFeatures()` computes the genomic distance and 
gets the precomputed features saved in the PrecomputedDataLight.db SQLite database.
Visit `vignette("Centre-vignette")` for more information.

All of the data in the CENTREprecomputed package can be accessed through ExperimentHub:

```{r, results='hide'}
library(ExperimentHub, quietly = TRUE)
```

```{r setup}
hub <- ExperimentHub()
eh <- query(hub, "CENTREprecomputed")
eh
```

The records EH9541-EH9545 are the example and test data for the CENTRE package.
Record EH9540 is the SQLite database which is accessed through `eh[["EH9540"]]` and
returns a CENTREprecompDb object or through `CENTREprecomputed::CENTREprecompDb`

## The CENTREprecompDb object

The R object to represent the precomputed database is `CENTREprecompDb`. 
To get the slots for class run `CENTREprecompDb` 
```{r, results='hide'}
CENTREprecomputed::CENTREprecompDb
```

There are three tables inside the database: 
- `combinedTestData`: -log transformed p-values of the Wilcoxon rank sum tests.
- `crup_cor`: correlations of CRUP-EP scores and CRUP-PP scores across cell-types.
- `metadata`: metadata for the ExperimentHub

For more information check `vignette("Centre-vignette")` or the 
[CENTRE publication](https://academic.oup.com/bioinformatics/article/39/11/btad687/7429396?searchresult=1) 

The database can be used as follows: 
```{r}
conn <- RSQLite::dbConnect(CENTREprecomputed::CENTREprecompDb@conn)
RSQLite::dbGetQuery(conn, "SELECT * from metadata")
RSQLite::dbDisconnect(conn) # don't forget to disconnect
```

